My title

### 2024-02-13 outputs/paper/paper.qmd
paper update

In this study, we developed a unique dataset by carefully selecting and combining data from the Household Pulse Survey, available from the U.S. Census Bureau for weeks 1 to 12. This process involved choosing key variables that were crucial for our research. We aimed to analyze the connection between economic changes, particularly the loss of employment income, and their impact on educational outcomes, focusing specifically on school passing rates. This helped us to understand the relationship between these economic factors and educational performance. To ensure consistency, we standardized terminologies and measurements, and aligned variables such as timeframes and demographic categories across the datasets. For example, we combined the state score data with the weekly household data, aligned variables relevant to our study. The merged data file was thereafter saved as a CSV file to study the trends later on.

# Results
In the Results section of our study, we first visualized the distribution of learning models across states using box plots. The box plot for in-person learning [@box_plot_inperson] revealed a range of engagement across states, with Virginia showing a median of 0 percentage in-person learning during 2019 to 2021, whereas Wyoming having a median of approximately 80 percent in-person learning. The virtual learning model box plot [@box_plot_virtual] showed a significant number of outliers, suggesting that certain states had districts with a notably high share of virtual learning.The states Wyoming and Rhode Island had a median of 0 percent virtual learning whereas Virginia had highest median of virtual learning.  Lastly, the hybrid learning model [@box_plot_hybrid] box plot displayed variability, with some states having a wide interquartile range, showing a diverse adoption of this learning model. However, Colorado had a median of 0 percent adoption of hybrid learning model relative to other states. These visual insights set the foundation for further statistical examination in subsequent analyses.

>>>>

In this study, we created a new dataset by carefully selecting and combining data from the Household Pulse Survey, available from the U.S. Census Bureau for weeks 1 to 12. This process involved choosing key variables that were crucial for our research. We aimed to analyze the connection between economic changes, particularly the loss of employment income, and their impact on educational outcomes, focusing specifically on school passing rates. This helped us to understand the relationship between these economic factors and educational performance. To ensure consistency, we standardized terminologies and measurements, and aligned variables such as timeframes and demographic categories across the datasets. For example, we combined the state score data with the weekly household data, aligned variables relevant to our study. The merged data file was thereafter saved as a CSV file to study the trends later on.

# Results
In the Results section of our study, our analysis discusses two key geographical representations:

1. Passing Rate Trends Over Different Years and Subjects: Figue [@fig] shows the decline in passing rates in English Language Arts (ELA) and Mathematics from 2016 to 2021, depicting a consistent downward trend across both subjects especially during pandemic period from 2019 to 2021.

2. Variations in Passing Rates Between Different States: The box plot comparison [@fig2] across states showcases the wide range of passing rates, with some states showing a wide spread, which indicates the  variability in performance within those states.

Building on these overviews, we visualized the distribution of learning models across states using box plots. The box plot for in-person learning [@box_plot_inperson] revealed a range of engagement across states, with Virginia showing a median of 0 percentage in-person learning during 2019 to 2021, whereas Wyoming having a median of approximately 80 percent in-person learning. The virtual learning model box plot [@box_plot_virtual] showed a significant number of outliers, suggesting that certain states had districts with a notably high share of virtual learning.The states Wyoming and Rhode Island had a median of 0 percent virtual learning whereas Virginia had highest median of virtual learning.  Lastly, the hybrid learning model [@box_plot_hybrid] box plot displayed variability, with some states having a wide interquartile range, showing a diverse adoption of this learning model. However, Colorado had a median of 0 percent adoption of hybrid learning model relative to other states. These visual insights set the foundation for further statistical examination in subsequent analyses.
